Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-07-29 tex/MesnardoBarba2019.tex
Fix typo "relatively" -> "relative"

\begin{table}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{Time-averaged force coefficients on the snake model at Reynolds number $2000$ and angle of attack $35^o$ for the two- and three-dimensional configurations. (We average the force coefficients between $40$ and $80$ time units of flow simulation and report the relatively difference of the 2D values with respect to the 3D ones.)}
    \label{tab:force_coefficients}
    \centering
    \begin{tabular}{cll}
        Case & $<C_D>$ & $<C_L>$ \\
        \hline
        3D & $0.8390$ & $1.5972$ \\
        2D & $1.1567$ ($+37.9\%$) & $1.8279$ ($+14.4\%$) \\
        \hline
    \end{tabular}
\end{table}

>>>>

\begin{table}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{Time-averaged force coefficients on the snake model at Reynolds number $2000$ and angle of attack $35^o$ for the two- and three-dimensional configurations. (We average the force coefficients between $40$ and $80$ time units of flow simulation and report the relative difference of the 2D values with respect to the 3D ones.)}
    \label{tab:force_coefficients}
    \centering
    \begin{tabular}{cll}
        Case & $<C_D>$ & $<C_L>$ \\
        \hline
        3D & $0.8390$ & $1.5972$ \\
        2D & $1.1567$ ($+37.9\%$) & $1.8279$ ($+14.4\%$) \\
        \hline
    \end{tabular}
\end{table}
